TOI based ProVisioNet

### 2021-09-13 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
R script TOI AOI

# df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

# df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

@@

@@

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Duration

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

## Start

```{r}
cor.test(x = df_cappa_start$Start_of_interval_AP,
     y = df_cappa_start$Start_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_start,
               Start_of_interval_AP,
               Start_of_interval_MK
               )
    )

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

>>>>

@@

# long format for plotting
dur_event_long  <- df_cappa_dur_aggr %>% gather(TOI, Duration)

@@
